Game theoretical concepts have been utilized to analyze problems for millennia, long
before game theory was a formally-defined field. One interesting example is that the Talmud, the Jewish holy book that provides the basis for Jewish law, prescribes solutions
for allocation of disputed resources that confounded scholars until the 1980s when mathematicians Robert Aumann and Michael Maschler solved the problem using the tools of
modern game theory. As it turns out, the solution given by the Talmud is to split the
disputed amount equally. Another example is when James Madison considered the effects of different taxation systems with game theoretical concepts. The list goes on, as
conflict resolution and strategic decision-making have been important issues throughout
all of human history.
The first work that brought about game theory as a formal field of mathematics
was Hungarian mathematician John von Neumann’s paper The Theory of Games in 1928. This paper had three major results. The first was reducing a game to the cases where
each player knows either everything or nothing about the other player’s previous moves.
He also proved the minimax theorem for two person zero-sum games, and he analyzed
three person zero-sum games.
Economist Oskar Morgenstern connected with von Neumann in 1938, and the
two then worked together on Theory of Games and Economic Behavior, published in
1944. This work was huge in the development of game theory. They expanded on von
Neumann’s previous work with an in-depth analysis of situations where players have only
partial knowledge of other players’ previous decisions, whereas The Theory of Games made
the assumption that players knew either everything or nothing about previous decisions.
They also expanded the definition of payoffs; previously payoffs were generally considered
to be only monetary, but von Neumann and Morgenstern developed the theory of utility,
which is still used today in many fields such as economics.
Since von Neumann and Morgenstern laid the foundation for game theory, it has
15
been added to by many mathematicians, such as John Nash in the 1950s. However, the
main development over the following decades was increasingly widespread application to
many fields. While certainly important in the field of economics, the use of game theory
has expanded to extensive use in biology, and it is also very important to the development
of military strategy. Interestingly, the five game theorists who have won the Nobel Prize
for economics also worked as advisors to the Pentagon over the courses of their careers. Game theory has also been applied in fields such as computer science and moral
philosophy.